---
output:
  bookdown::pdf_document2:
      latex_engine: xelatex
      number_sections: false
      toc: false
mainfont: "Times New Roman"
geometry: margin = 1in
spacing: double
fontsize: 11pt
editor_options:
  markdown:
    wrap: sentence
bibliography: "supp_info_s5.bib"
csl: https://raw.githubusercontent.com/marlonecobos/kuenm/master/ecography.csl
link-citations: yes
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}\doublespacing
   - \usepackage{parskip}
   - \setlength{\parindent}{4em}
   - \setlength{\parskip}{0em}
   - \usepackage{caption}
   - \usepackage{pdflscape}
   - \newcommand{\blandscape}{\begin{landscape}}
   - \newcommand{\elandscape}{\end{landscape}}
---

```{r setup, include=FALSE}
library(ggplot2)
library(ggpubr)
library(sf)
library(raster)
library(exactextractr)
library(data.table)
library(phytools)
library(PhyloMeasures)
library(dplyr)
library(tidyr)
library(reshape2)
library(scales)
library(purrr)
library(robust)
library(latex2exp)

knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE,
                      fig.height = 5,
                      fig.width = 5,
                      fig.align = "center",
                      cache.lazy = TRUE)

source("~/chapter-PaleoClimPoolCommDivPhyloStruct/R1/scripts/S0_fun_ses.opt.rarefaction.phylostr.R")

source("~/chapter-PaleoClimPoolCommDivPhyloStruct/R1/scripts/S0_fun_bootstrap_logit_GLM_uncondition_quant.R")

source("~/chapter-PaleoClimPoolCommDivPhyloStruct/R1/scripts/S0_fun_ggplot_theme_map.R")


glm.boot.AllScales.NRI.ClimStab.Div.quantiles.075 <- readRDS("~/chapter-PaleoClimPoolCommDivPhyloStruct/R1/data/matrices/glm.boot.AllScales.NRI.ClimStab.Div.quantiles.075.RDS")
glm.boot.AllScales.NTI.ClimStab.Div.quantiles.075 <- readRDS("~/chapter-PaleoClimPoolCommDivPhyloStruct/R1/data/matrices/glm.boot.AllScales.NTI.ClimStab.Div.quantiles.075.RDS")

glm.boot.AllScales.NRI.NTI.ClimStab.Div.quantiles.075 <- bind_rows(
  data.frame(glm.boot.AllScales.NRI.ClimStab.Div.quantiles.075[, 2:5],
             PhyloStructure = "NRI") %>%
    reshape2::melt( 
      id.vars = c("SamplingPool", "PhyloStructure"),
      variable.name = "variable",
      value.name = "estimate"),
  
  data.frame(glm.boot.AllScales.NTI.ClimStab.Div.quantiles.075[, 2:5],
             PhyloStructure = "NTI") %>%
    reshape2::melt( 
      id.vars = c("SamplingPool", "PhyloStructure"),
      variable.name = "variable",
      value.name = "estimate")
)

glm.boot.AllScales.NRI.NTI.ClimStab.Div.quantiles.075$SamplingPool <- factor(glm.boot.AllScales.NRI.NTI.ClimStab.Div.quantiles.075$SamplingPool,
                                                                            levels = c(
                                                                              "Global sampling",
                                                                              "Hemispheric sampling",
                                                                              "Realm sampling",
                                                                              "Plate sampling",
                                                                              "Biome sampling",
                                                                              "Ecoregion sampling"),
                                                                            labels = c(
                                                                              "Global~sampling",
                                                                              "Hemispheric~sampling",
                                                                              "Realm~sampling",
                                                                              "Plate~sampling",
                                                                              "Biome~sampling",
                                                                              "Ecoregion~sampling"
                                                                            )
)


glm.boot.AllScales.NRI.NTI.ClimStab.Div.quantiles.075$PhyloStructure <- as.factor(glm.boot.AllScales.NRI.NTI.ClimStab.Div.quantiles.075$PhyloStructure)

levels(glm.boot.AllScales.NRI.NTI.ClimStab.Div.quantiles.075$PhyloStructure)

levels(glm.boot.AllScales.NRI.NTI.ClimStab.Div.quantiles.075$PhyloStructure) <- c(TeX("$Pr(NRI_{Q75}=1)$"), TeX("$Pr(NTI_{Q75}=1)$"))
# TeX('$Pr(NRI_{Q_{90}}=1)$')
```

## Study

## The historical and contemporary processes driving global phylogenetic structure – the case of bat communities\

## Supplementary Information 7

### Appendix S7. Effects of historical climatic stability and _in situ_ diversification rates in the odds of phylogenetic community structure from the upper quartile

When testing hypotheses H2 and H3 inferentially, we also used the upper unconditional quartile (_i.e._, the 75th percentile) to obtain the binary outcomes for the phylogenetic structure (either NRI or NTI) in each community (see Methods). With this, a value of one was assigned to a given community if it belonged to the 75th percentile of phylogenetic relatedness, otherwise a value of zero was assigned to them. We then applied conditionally unbiased bounded influence robust logistic regressions in which the response variable was the vector of binary outcomes (ones and zeros) representing relatively high or low phylogenetic structure (separately for NRI and NTI) and the predictors were z-score standardized values (_i.e._, to have mean zero and variance one) of historical change in temperature, historical change in precipitation and _in situ_ net diversification rates. With this, we could estimate the relative importance of each predictor within a single model. To estimate confidence intervals for each predictor, we used a bootstrap approach based on 1,000 resamples of 2,500 random communities each. This approach allowed us to explicitly test how changes in historical climatic stability and _in situ_ diversification rates independently increased (or decreased) the log-odds (the logistic response) of a community being composed of highly phylogenetically related species (in relation to the 75th percentile).

These results were highly qualitatively similar to the ones using the 90th percentile of phylogenetic relatedness as cut-off, with the exception for the effects of historical change in temperature at the global sampling geographical extent (see Figures 5 and S7.1, and Tables 2 and S7.1). This highlights the variation in importance of temperature stability across different portions of the gradient of phylogenetic relatedness in biological communities.


\newpage

\blandscape

### Figures

\noindent
**Figure S7.1.** Influence of historical legacies on phylogenetic structure of bats across different geographical extents. Distributions represent boxplot of bootstrapped logistic regression coefficients using binary outcomes (at the 90th percentile) for the indices of phylogenetic community relatedness ($Pr(\mathsf{NRI_{Q75}}=1)$) and $Pr(\mathsf{NTI_{Q75}}=1)$) as response variables (in separate models) and the z-score standardized (with values transformed to have mean zero and one-unit variance) historical change in temperature, historical change in precipitation and in situ net diversification rates as predictive variables. Phylogenetic structure of bat communities was measured through the net relatedness index (NRI) and the nearest taxon index (NTI) at each geographical extent. In situ net diversification rates were obtained by subtracting the difference between community-weighted means weight-standardized for speciation and extinction rates. Paleoclimatic legacies for each bat community were obtained as the historical change in climate since the last glacial maximum (LGM); specifically, the mean annual temperature or logarithm of the mean annual precipitation from the contemporary period minus the estimated mean annual temperature or logarithm of the mean annual precipitation from 22,000 years ago.

```{r plot-glm-1, echo=FALSE, fig.dim=c(5*6, 5), message=FALSE, warning=FALSE, fig.align = 'center', dpi = 250}

##### Figure creation #####

# q = 0.75 ######

(fig.wrap.boot.AllScales.NRI.NTI.ClimStab.Div.quantile.075 <- ggplot(data = glm.boot.AllScales.NRI.NTI.ClimStab.Div.quantiles.075,
                                                                    aes(x = estimate,
                                                                        y = variable)
) +
    geom_boxplot(
      lwd = 0.2,
      outlier.size = 1,
      outlier.stroke = 0.2,
      aes(fill = SamplingPool, 
          colour = SamplingPool
      ))  +
    ggsci::scale_fill_uchicago(alpha = 0.8) +
    ggsci::scale_colour_uchicago() +
    labs(y = "",
         x = "Partial bootstrapped coefficients") +
    scale_y_discrete(
      labels = c("diff.AnnTemp.LGM_cur" = "Historical change in temperature", 
                 "diff.log.AnnPrec.log.LGM_cur" = "Historical change in precipitation",
                 "netDiv_CWM_std_tw_rs_1" = "_In situ_ diversification rates")
    ) +
    
    # Add white line on top (Inf) of the plot (ie, betweem plot and facet)
    # geom_vline(xintercept = Inf, 
    #            color = "white", 
    #            size = 10) +
    geom_vline(xintercept = 0,
               alpha = 0.4) +
    facet_grid(PhyloStructure ~ SamplingPool,
               # scales = "free",
               switch = "y",
               labeller = label_parsed
    ) +
    # facet_wrap(SamplingPool~PhyloStructure,
    #            nrow = 6,
    #            ncol = 2,
    #            strip.position = c("top",
    #                               "right")) +
    
    theme_boot_quant() +
    theme(
      plot.margin = unit(
        c(1.2, # top
          1, 
          1.2,
          0.5), "lines"),
      panel.spacing.x = unit(1, "lines"),
      panel.spacing.y = unit(1.5, "lines"),
      strip.placement = "outside",
      #      strip.background = element_rect(size = 1),
      strip.text.y = element_text(margin = margin(t = 0, 
                                                  r = 2, 
                                                  b = 0, 
                                                  l = 2, "mm")),
      strip.text.x = element_text(margin = margin(t = 0, 
                                                  r = 0, 
                                                  b = 2, 
                                                  l = 0, "mm"),
                                  size = 17),
      axis.text.x = ggtext::element_markdown( 
        size = 15,
        # angle = 90, 
        vjust = 1, 
        hjust = 0.5,
        face = "bold"),
      axis.text.y = ggtext::element_markdown( 
        size = 15,
        hjust = 1),
      axis.title = element_text(size = 16),
      legend.position = "none"
      
    )
)
```
\def\fillandplacepagenumber{%
 \par\pagestyle{empty}%
 \vbox to 0pt{\vss}\vfill
 \vbox to 0pt{\baselineskip0pt
   \hbox to\linewidth{\hss}%
   \baselineskip\footskip
   \hbox to\linewidth{%
     \hfil\thepage\hfil}\vss}}

\fillandplacepagenumber

\elandscape

\newpage

\blandscape

\noindent 
**Table S7.1. ** Influence of climatic legacies and _in situ_ diversification rates on the phylogenetic structure of bat communities across different geographical extents. Regression coefficients (and ± 95% bootstrap-based confidence intervals) for the robust logistic generalized linear models using binary outcomes (at the 90th percentile) for the indices of phylogenetic community relatedness ($Pr(\mathsf{NRI_{Q975}}=1)$) and $Pr(\mathsf{NTI_{Q75}}=1)$) as response variables (in separate models) and the standardized (mean zero and variance one) historical change in temperature, historical change in precipitation and _in situ_ net diversification rates as predictive variables. The phylogenetic structure of bat communities was measured through the net relatedness index (NRI) and the nearest taxon index (NTI) at each geographical extent. _In situ_ net diversification rates were obtained by subtracting the difference between community-weighted means weight-standardized for speciation and extinction rates. Historical change in climate for each bat community was obtained as the difference between the contemporary climate (either temperature or the logarithm of precipitation) from the estimated climate from the last glacial maximum (22,000 years ago).


\captionsetup[table]{labelformat = empty}
```{r log-inv-res-table-1, echo = FALSE, message = FALSE, warning = FALSE}
library(gtsummary)
library(huxtable)
library(mosaic)

mean_exp <- function(data, ...){
  dplyr::tibble(
    mean_exp. = exp(mean(data$estimate, 
                         na.rm = TRUE)),
    mean = mean(data$estimate, na.rm = TRUE),
    ci.lower = confint(data$estimate,
                       level = 0.95,
                       method = "stderr")[,1],
    ci.upper = confint(data$estimate, 
                       level = 0.95,
                       method = "stderr")[,2]
    
  )
}

tbl_stack(
  list(
    data.frame(glm.boot.AllScales.NRI.ClimStab.Div.quantiles.075,
               PhyloStructure = "NRI") %>%
      reshape2::melt(id.vars = c("SamplingPool", "PhyloStructure"),
                      variable.name = "variable",
                      value.name = "estimate") %>%
      as.matrix() %>%
      as.data.frame() %>%
      mutate(estimate, estimate = as.numeric(estimate),
             variable, Variables = plyr::revalue(variable, 
                                                 c("X.Intercept." = "Intercept",
                                                   "diff.AnnTemp.LGM_cur" = "Historical change in temperature", 
                                                   "diff.log.AnnPrec.log.LGM_cur" = "Historical change in precipitation",
                                                   "netDiv_CWM_std_tw_rs_1" = "In situ diversification rates"
                                                 )
             ),
             SamplingPool, SamplingPool = factor(SamplingPool, levels = c(
               "Global sampling",
               "Hemispheric sampling",
               "Realm sampling",
               "Plate sampling",
               "Biome sampling",
               "Ecoregion sampling"
             ))) %>%
      mutate(estimate, 
             estimate = as.numeric(estimate),
             Variables, 
             Variables = factor(Variables, 
                                levels = c("Intercept",
                                            "Historical change in temperature",
                                            "Historical change in precipitation",
                                            "In situ diversification rates"
                                ))) %>%
      select(-variable, -PhyloStructure) %>%
      group_by(Variables, SamplingPool) %>%
      ungroup() %>%
      group_nest(Variables) %>%
      mutate(
        tbl = map2(
          Variables, data, 
          ~tbl_custom_summary(.y, 
                              by = SamplingPool, 
                              type = list(estimate ~ 'continuous'),
                              label = list(estimate = paste("", .x)), 
                              missing = "no",
                              statistic = "estimate" ~ "{mean} ({ci.lower}; {ci.upper})",
                              stat_fns = everything() ~ mean_exp
          )
        )
      ) %>%
      pull(tbl) %>%
      tbl_stack() %>%
      modify_footnote(all_stat_cols() ~ "Mean (Lower CI; Upper CI)") %>%
      bold_labels(),
    
    #
    #
    
    data.frame(glm.boot.AllScales.NTI.ClimStab.Div.quantiles.075,
               PhyloStructure = "NTI") %>%
      reshape2::melt( id.vars = c("SamplingPool", "PhyloStructure"),
                      variable.name = "variable",
                      value.name = "estimate") %>%
      as.matrix() %>%
      as.data.frame() %>%
      mutate(estimate, estimate = as.numeric(estimate),
             variable, Variables = plyr::revalue(variable, 
                                                 c("X.Intercept." = "Intercept",
                                                   "diff.AnnTemp.LGM_cur" = "Historical change in temperature", 
                                                   "diff.log.AnnPrec.log.LGM_cur" = "Historical change in precipitation",
                                                   "netDiv_CWM_std_tw_rs_1" = "In situ diversification rates"
                                                   
                                                 )),
             SamplingPool, SamplingPool = factor(SamplingPool, levels = c(
               "Global sampling",
               "Hemispheric sampling",
               "Realm sampling",
               "Plate sampling",
               "Biome sampling",
               "Ecoregion sampling"
             ))) %>%
      mutate(estimate, 
             estimate = as.numeric(estimate),
             Variables, 
             Variables = factor( Variables, 
                                 levels = c("Intercept",
                                            "Historical change in temperature",
                                            "Historical change in precipitation",
                                            "In situ diversification rates"
                                 ))) %>%
      select(-variable, -PhyloStructure) %>%
      group_by(Variables, SamplingPool) %>%
      ungroup() %>%
      group_nest(Variables) %>%
      mutate(
        tbl = map2(
          Variables, data, 
          ~tbl_custom_summary(.y, 
                              by = SamplingPool, 
                              type = list(estimate ~ 'continuous'),
                              label = list(estimate = paste("", .x)), 
                              missing = "no",
                              statistic = "estimate" ~ "{mean} ({ci.lower}; {ci.upper})",
                              stat_fns = everything() ~ mean_exp
          )
        )
      ) %>%
      pull(tbl) %>%
      tbl_stack() %>%
      modify_footnote(all_stat_cols() ~ "Mean (Lower CI; Upper CI)") %>%
      modify_caption(caption = "") %>%
      bold_labels() 
  ),
  group_header = c("NRI", 
                   "NTI")
) %>% 
  bold_labels() %>%
  as_hux_table() %>%      
  set_width(1.3) %>% 
  set_font_size(8) %>% 
  huxtable::theme_article(header_rows = TRUE, header_cols = TRUE) %>%
  set_caption(NA) %>%
  set_caption_pos("topleft")
# as_flex_table() %>%
# flextable::fontsize(size = 7, part = "all") %>%
# set_table_properties(layout = "autofit") %>%
# flextable::autofit() %>%
# flextable::fit_to_width(7.5)

```

\def\fillandplacepagenumber{%
  \par\pagestyle{empty}%
  \vbox to 0pt{\vss}\vfill
  \vbox to 0pt{\baselineskip0pt
    \hbox to\linewidth{\hss}%
    \baselineskip\footskip
    \hbox to\linewidth{%
      \hfil\thepage\hfil}\vss}}

\fillandplacepagenumber

\elandscape
