---
output:
  bookdown::pdf_document2:
      latex_engine: xelatex
      number_sections: false
      toc: false
mainfont: "Times New Roman"
geometry: margin = 1in
spacing: double
fontsize: 11pt
editor_options:
  markdown:
    wrap: sentence
bibliography: "supp_info_s3.bib"
csl: https://raw.githubusercontent.com/marlonecobos/kuenm/master/ecography.csl
link-citations: yes
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}\doublespacing
   - \usepackage{parskip}
   - \setlength{\parindent}{4em}
   - \setlength{\parskip}{0em}
---

```{r setup, include=FALSE}
library(ggplot2)
library(ggpubr)
library(phytools)
library(PhyloMeasures)
library(dplyr)
library(tidyr)
library(ks)
library(reshape2)
library(scales)

knitr::opts_chunk$set(echo = TRUE,
                      cache = TRUE)

source("~/chapter-PaleoClimPoolCommDivPhyloStruct/R1/scripts/SX_fun_ses.opt.rarefaction.phylostr.R")

MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div <- readRDS("~/chapter-PaleoClimPoolCommDivPhyloStruct/R1/data/matrices/MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div.rds")

MPD.MNTD.LatLong.AllScales.worldClimate.diff <- readRDS("~/chapter-PaleoClimPoolCommDivPhyloStruct/R1/data/matrices/MPD.MNTD.LatLong.AllScales.worldClimate.diff.rds")
```

```{r include=FALSE}
generate_community <- function(T,
                               preset_ncommunities, 
                               param = 1) {
  preset_nspecies <- length(T)
  repeat {
    E <- scale(rnorm(preset_ncommunities))
    T <- scale(T)
    # one trait, one environmental variable
    L <- matrix(data = 0, 
                nrow = preset_ncommunities, 
                ncol = preset_nspecies)
    for (j in 1:preset_nspecies) {
      L[, j] <- rbinom(preset_ncommunities, 
                       1, 
                       (1 / (1 + exp(-param * E * T[j]))))
    }
    n_species_c <- sum(colSums(L) != 0) #
    n_communities_c <- sum(rowSums(L) != 0)
    if ((n_species_c == preset_nspecies) & (n_communities_c == preset_ncommunities)) {
      break
    }
  }
  colnames(L) <- rownames(T)
  output <- list(L = L, E = E)
  return(output)
}

# Set seed to reproduce the same results

set.seed(123)

# Determine the number of species in the phylogenetic pool, which should match a
# hypothetical global pool

n.species <- 1000

# Simulare a pure-birth tree with n.species on it

large.tree <- pbtree(n = n.species, 
                     scale = 1)

# Obtain species names from the phylogenetic tree, which will be used to
# simulate ecological communities

species.names <- large.tree$tip.label

# Determine the number of ecological communities we would like to sample

n.communities <- 10000

# Determine the strength the environmental
# requirements of species

strength.Env.Phylo <- 5

# Sinulate a trait under Brownian motion in the phylogenetic tree 

T.phylo <- fastBM(large.tree, 
                  sig2 = 0.1)

# Simulate a large scale region containing n.communities communities

species.data.region.sim <- generate_community(T = T.phylo, 
                                              preset_ncommunities = n.communities, 
                                              param = strength.Env.Phylo)

# Obtain the presence-absence matrix element This matrix comprises the largest
# spatial scale region, from which we will subset smaller scale regions

species.data.region <- species.data.region.sim$L

# Subset a smaller scale region containing the first subset.n.species (columns)
# and the first subset.n.comm (rows)

subset.n.species <- 250
subset.n.comm <- 5000

subset.species.data.region <- species.data.region[1:subset.n.comm, 
                                                  1:subset.n.species]

# We will now create a gradient of phylogenetic sampling frames that increments
# species to the local subset.species.data.region species pool.

# This is done by first subsetting all species names that are not part of the
# subset.species.data.region pool, then sampling n species names from it, and
# then adding these names to the species names that are within the
# subset.species.data.region; and then storing it to the larger.pool object.

# The original phylogenetic tree is then pruned to the larger.pool, so it
# contains the sampling frame that we have created.

# Finally, to obtain and compare how the phylogenetic relatedness of the
# communities is in relation to a given phylogenetic sampling frame, we apply two
# approaches:

# The first approach is the traditional method for calculating standardized
# effect sizes for the phylogenetic relatdness (from Webb 2000).

# The second approach consists of applying rarefaction in the calculation of
# phylogenetic relatedness for the ecological communities. In this rarefaction
# approach, we randomly subsample (rarefy) species from the phylogenetic pool to
# a subset of size m multiple times and calculate the average of standardized
# effect sizes of phylogenetic relatdness of those subsets.

extra.species.for.pool <- seq(50, 
                              c(n.species - subset.n.species), 
                              by = 50)

mpd.pool.comparisons <- data.frame()

# n = extra.species.for.pool[1]

for(n in extra.species.for.pool){
  larger.pool <- large.tree$tip.label[! large.tree$tip.label %in% colnames(subset.species.data.region)] %>%
    sample(n) %>%
    c(colnames(subset.species.data.region))
  
  smaller.tree <- keep.tip(large.tree, 
                           larger.pool)
  
  if(round(length(smaller.tree$tip.label)/3) < subset.n.species){
    
    mpd.sampling.pool <- opt.rarefaction.mpd(n.species.rarefac = round(length(smaller.tree$tip.label)/3), 
                                             phylo.tree = smaller.tree,
                                             species.data = subset.species.data.region,
                                             n.rep = 1000, 
                                             n.cores = 8)
    
    mpd.sampling.pool$ses.mpd.z.query.rarefac$pool.size <- length(smaller.tree$tip.label)
    
    mpd.pool.comparisons <- rbind(mpd.pool.comparisons, mpd.sampling.pool$ses.mpd.z.query.rarefac)
  }
}


mntd.pool.comparisons <- data.frame()

for(n in extra.species.for.pool){
  
  larger.pool <- large.tree$tip.label[! large.tree$tip.label %in% colnames(subset.species.data.region)] %>%
    sample(n) %>%
    c(colnames(subset.species.data.region))
  
  smaller.tree <- keep.tip(large.tree, 
                           larger.pool)
  if(round(length(smaller.tree$tip.label)/3) < subset.n.species){
    mntd.sampling.pool <- opt.rarefaction.mntd(n.species.rarefac = round(length(smaller.tree$tip.label)/3), 
                                               phylo.tree = smaller.tree,
                                               species.data = subset.species.data.region,
                                               n.rep = 1000, 
                                               n.cores = 8)
    
    mntd.sampling.pool$ses.mntd.z.query.rarefac$pool.size <- length(smaller.tree$tip.label)
    
    mntd.pool.comparisons <- rbind(mntd.pool.comparisons, mntd.sampling.pool$ses.mntd.z.query.rarefac)
  }
}

mpd.fixed.pool.comparisons <- data.frame()

# n = extra.species.for.pool[1]

for(n in extra.species.for.pool){
  
  larger.pool <- large.tree$tip.label[! large.tree$tip.label %in% colnames(subset.species.data.region)] %>%
    sample(n) %>%
    c(colnames(subset.species.data.region))
  
  smaller.tree <- keep.tip(large.tree, 
                           larger.pool)
  if(100 < subset.n.species){    
    mpd.sampling.pool <- opt.rarefaction.mpd(n.species.rarefac = 100, 
                                             phylo.tree = smaller.tree,
                                             species.data = subset.species.data.region,
                                             n.rep = 1000, 
                                             n.cores = 8)
    
    mpd.sampling.pool$ses.mpd.z.query.rarefac$pool.size <- length(smaller.tree$tip.label)
    
    mpd.fixed.pool.comparisons <- rbind(mpd.fixed.pool.comparisons, mpd.sampling.pool$ses.mpd.z.query.rarefac)
  }
}


mntd.fixed.pool.comparisons <- data.frame()

for(n in extra.species.for.pool){
  
  larger.pool <- large.tree$tip.label[! large.tree$tip.label %in% colnames(subset.species.data.region)] %>%
    sample(n) %>%
    c(colnames(subset.species.data.region))
  
  smaller.tree <- keep.tip(large.tree, 
                           larger.pool)
  if(100 < subset.n.species){    
    mntd.sampling.pool <- opt.rarefaction.mntd(n.species.rarefac = 100, 
                                               phylo.tree = smaller.tree,
                                               species.data = subset.species.data.region,
                                               n.rep = 1000, 
                                               n.cores = 8)
    
    mntd.sampling.pool$ses.mntd.z.query.rarefac$pool.size <- length(smaller.tree$tip.label)
    
    mntd.fixed.pool.comparisons <- rbind(mntd.fixed.pool.comparisons, mntd.sampling.pool$ses.mntd.z.query.rarefac)
  }
}
```


```{r echo=FALSE, eval = TRUE}
NRI.fixed.pool.size.rarefac<- ggplot(mpd.fixed.pool.comparisons, 
                                     aes(x = pool.size, 
                                         y = nri.rarefac.mean, 
                                         group = pool.size)) +
  geom_boxplot() +
  scale_y_continuous() +
  geom_hline(yintercept = 0,
             alpha = 0.4) +
  labs(y = expression(NRI[raref[FIX]]), 
       x = "Species in the phylogeny") +
  theme_minimal() +
  theme_minimal(base_size = 20) +
  theme(strip.background = element_rect(fill = "white",
                                        linetype = NULL,
                                        color = "white"),
        strip.text = element_text(color = "black",
                                  face = "bold",
                                  size = 15),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        axis.title = element_text(size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        legend.title.align = 0.5,
        legend.margin=margin(0, 0, 0, 0),
        legend.box.margin=margin(-5, -5, 2, -5)
  )


NTI.fixed.pool.size.rarefac<- ggplot(mntd.fixed.pool.comparisons, aes(x = pool.size, 
                                                                      y = nti.rarefac.mean, 
                                                                      group = pool.size)) +
  geom_boxplot() +
  scale_y_continuous() +
  geom_hline(yintercept = 0,
             alpha = 0.4) +
  labs(y = expression(NTI[raref[FIX]]), 
       x = "Species in the phylogeny") +
  theme_minimal(base_size = 20) +
  theme(strip.background = element_rect(fill = "white",
                                        linetype = NULL,
                                        color = "white"),
        strip.text = element_text(color = "black",
                                  face = "bold",
                                  size = 15),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        axis.title = element_text(size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        legend.title.align = 0.5,
        legend.margin=margin(0, 0, 0, 0),
        legend.box.margin=margin(-5, -5, 2, -5)
  )



NRI.pool.size <- ggplot(mpd.pool.comparisons, aes(x = pool.size, 
                                                  y = nri.sec, 
                                                  group = pool.size)) +
  geom_boxplot() +
  scale_y_continuous() +
  geom_hline(yintercept = 0,
             alpha = 0.4) +
  labs(y = expression(NRI), 
       x = "Species in the phylogeny") +
  theme_minimal() +
  theme_minimal(base_size = 20) +
  theme(strip.background = element_rect(fill = "white",
                                        linetype = NULL,
                                        color = "white"),
        strip.text = element_text(color = "black",
                                  face = "bold",
                                  size = 15),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        axis.title = element_text(size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        legend.title.align = 0.5,
        legend.margin=margin(0, 0, 0, 0),
        legend.box.margin=margin(-5, -5, 2, -5)
  )


NRI.pool.size.rarefac<- ggplot(mpd.pool.comparisons, aes(x = pool.size, 
                                                         y = nri.rarefac.mean, 
                                                         group = pool.size)) +
  geom_boxplot() +
  scale_y_continuous() +
  geom_hline(yintercept = 0,
             alpha = 0.4) +
  labs(y = expression(NRI[raref[REL]]), 
       x = "Species in the phylogeny") +
  theme_minimal() +
  theme_minimal(base_size = 20) +
  theme(strip.background = element_rect(fill = "white",
                                        linetype = NULL,
                                        color = "white"),
        strip.text = element_text(color = "black",
                                  face = "bold",
                                  size = 15),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        axis.title = element_text(size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        legend.title.align = 0.5,
        legend.margin=margin(0, 0, 0, 0),
        legend.box.margin=margin(-5, -5, 2, -5)
  )


NTI.pool.size <- ggplot(mntd.pool.comparisons, aes(x = pool.size, 
                                                   y = nti.sec, 
                                                   group = pool.size)) +
  geom_boxplot() +
  scale_y_continuous() +
  geom_hline(yintercept = 0,
             alpha = 0.4) +
  labs(y = expression(NTI), 
       x = "Species in the phylogeny") +
  theme_minimal(base_size = 20) +
  theme(strip.background = element_rect(fill = "white",
                                        linetype = NULL,
                                        color = "white"),
        strip.text = element_text(color = "black",
                                  face = "bold",
                                  size = 15),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        axis.title = element_text(size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        legend.title.align = 0.5,
        legend.margin=margin(0, 0, 0, 0),
        legend.box.margin=margin(-5, -5, 2, -5)
  )


NTI.pool.size.rarefac<- ggplot(mntd.pool.comparisons, aes(x = pool.size, 
                                                          y = nti.rarefac.mean, 
                                                          group = pool.size)) +
  geom_boxplot() +
  scale_y_continuous() +
  geom_hline(yintercept = 0,
             alpha = 0.4) +
  labs(y = expression(NTI[raref[REL]]), 
       x = "Species in the phylogeny") +
  theme_minimal(base_size = 20) +
  theme(strip.background = element_rect(fill = "white",
                                        linetype = NULL,
                                        color = "white"),
        strip.text = element_text(color = "black",
                                  face = "bold",
                                  size = 15),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_text(face = "bold"),
        axis.title = element_text(size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        legend.title.align = 0.5,
        legend.margin=margin(0, 0, 0, 0),
        legend.box.margin=margin(-5, -5, 2, -5)
  )


### Combining plots into a single figure ###

fig.NRI.NTI.Realm.boxplot.phyloSampling <- ggarrange(
  NRI.pool.size +
    theme(axis.title.x = element_blank()), 
  NTI.pool.size+
    theme(axis.title.x = element_blank()),
  NRI.pool.size.rarefac+
    theme(axis.title.x = element_blank()),
  NTI.pool.size.rarefac+
    theme(axis.title.x = element_blank()),
  NRI.fixed.pool.size.rarefac,
  NTI.fixed.pool.size.rarefac,
  labels = c("A", "B", "C", "D", "E", "F"),
  ncol = 2, nrow = 3,
  widths = c(1, 1),
  heights = c(1, 1.1),
  align = "v",
  common.legend = TRUE,
  legend = "bottom"
)
```


### Study
### The historical and contemporary processes driving global phylogenetic structure – the case of bat communities\

### Supplementary Information 3

### Appendix S3. Assessing and correcting for the sampling frame size bias on indices of community phylogenetic relatedness

### Sampling frame size-dependence in indices for phylogenetic community structure

The magnitude of standardized effect sizes of indices for phylogenetic community structure may increase with the number of species in the phylogeny (or size of the sampling frame) used to compute the null models pertinent to these metrics [@sandel2018e]. This bias requires that studies comparing standardized effect sizes of phylogenetic relatedness between biological communities to assess whether these comparisons hold after correcting for this problem.

One possible approach to correct for the sampling frame size bias is to repeatedly randomly subsample (_i.e._ rarefy) the community matrix to smaller sampling frame sizes, and then to calculate the average indices for phylogenetic community structure [here, the net relatedness index (NRI) and the nearest taxon index (NTI); see Methods] across the rarefied subset [see @sandel2018e]. The resulting index from this procedure should show a negligible relationship with the size of the sampling frame or the phylogeny. Because the original size of the sampling frame is decreased, this correction comes at the expense of losing power intrinsic to the rarefaction procedure [@sandel2018e]. The information from sampling frames that have less species than the size chosen for the subsampling procedure is also lost.

### Bias-correction robustness and implementation 

We begin by demonstrating the influence of sampling frame sizes on the phylogenetic community structure indices and the robustness of the bias-correction approach with a simple set of simulations. We generated 10000 communities and a random pure-birth tree, both containing 1000 species, which represents the broad-scale sampling frame. We then subset 5000 communities and 250 species from the broad-scale sampling frame.

Then, for sampling frame sizes increasing from 250 species to 1000 species, in increments of 50 species, we iteratively calculated the uncorrected net relatedness index (NRI) and the nearest taxon index (NTI) of these simulated communities, as well as two indices corrected through rarefaction -- $\mathsf{NRI_{raref_{FIX}}}$, $\mathsf{NTI_{raref_{FIX}}}$, $\mathsf{NRI_{raref_{REL}}}$ and $\mathsf{NTI_{raref_{REL}}}$ --, which differed in the number of species subsampled in each computation.

$\mathsf{NRI_{raref_{LOW}}}$ and $\mathsf{NTI_{raref_{LOW}}}$ were computed by rarefying the community presence-absence matrix to the lowest species pool possible for that sampling frame extent, and then computing NRI and NTI on this matrix (as in Sandel, 2018).

$\mathsf{NRI_{raref_{REL}}}$ and $\mathsf{NTI_{raref_{REL}}}$ rarefy the community presence-absence matrix to one third of the number of species in the sampling frame of that region. This procedure removed less communities from the computation and allowed for less loss of power and loss of information inherent from the rarefaction procedure.

To assess whether the results from our study still held after correcting for the influence of the size of sampling frames in the standardized effect sizes index values for phylogenetic community structure, we recalculated the NRI and NTI of bat communities using the second bias-correction approach, which ensures less loss information but still corrects for the influence of sampling frame size. We repeated the rarefaction procedure 1000 times and reproduced the figures addressing the hypothesis testing from our manuscript using the separate averages of both rarefaction indices across their replicates. 

The interpretation of the rarefied indices follow the same ones for NRI and NTI (see Methods in the main document; Webb, 2000).

We performed these procedures using R and RStudio [@rcoreteamLanguageEnvironmentStatistical2019; @rstudioteam2020], with the help of functions from the `ape` [@paradis2019ba], `picante` [@kembel2010b], `PhyloMeasures` [@tsirogiannis2017], `tidyverse` [@wickham2019joss] packages. See Appendix S1 for complementary information on tools used in this study.

### Rarefaction corrects for sampling frame size bias in both simulations and in empirical data

As demonstrated in Sandel [-@sandel2018e], the traditional community phylogenetic relatedness indices (NRI and NTI) increased with the size of the phylogenetic sampling frame in our simulated communities [as shown by $\mathsf{NRI}$ (net relatedness index) and $\mathsf{NTI}$ (nearest taxon index); Figure S3.1 A and B]. However, the rarefaction-based calculation of phylogenetic relatedness effectively removes the sampling frame size bias in the simulations (see Figure S3.1 C-F). $\mathsf{NRI_{raref_{LOW}}}$ and $\mathsf{NTI_{raref_{LOW}}}$, which fix the size of sampling frames to the smallest sample,

As expected, the rarefied net relatedness index ($\mathsf{NRI_{raref_{REL}}}$) and nearest taxon index ($\mathsf{NTI_{raref_{REL}}}$) for bat communities were closer to zero, but highly correlated with their respective unrarefied indices for phylogenetic relatedness.

All figures we reproduced with the rarefied NRI and NTI indices (Figures S3.2, S3.3, S3.4 and S3.5) had similar patterns to those we observed in the figures from the main manuscript (Figures 2, 3, 4 and 5). 

For the purposes of simplification and to avoid the loss of information introduced by the rarefaction procedure, we use the unrarefied values for NRI and NTI in the main manuscript.

## References for Supporting Information 4

<div id="refs"></div>

## Figures

\noindent 
**Figure S3.1** The size of the phylogenetic sampling frame influences community phylogenetic relatedness index values of simulated communities [as shown by $\mathsf{NRI}$ (net relatedness index) and $\mathsf{NTI}$ (nearest taxon index); A and B]. Rarefaction with both fixed-size sub-sampling [$\mathsf{NRI_{raref_{FIX}}}$ and $\mathsf{NTI_{raref_{FIX}}}$; C and D] and relative-size sub-sampling [$\mathsf{NRI_{raref_{REL}}}$ and $\mathsf{NTI_{raref_{REL}}}$; E and F] removes the sampling frame size-dependence.

```{r echo=FALSE, eval = TRUE, fig.width = 12, fig.height = 18, fig.align = "center"}
fig.NRI.NTI.Realm.boxplot.phyloSampling
```

\noindent 
**Figure S3.2.** Realm-comparison of the sampling frame size bias-corrected phylogenetic structure of bat assemblages – measured through the (A) rarefied net relatedness index ($\mathsf{NRI_{raref_{REL}}}$) and (B) nearest taxon index ($\mathsf{NTI_{raref_{REL}}}$) – across a gradient of sampling frame spatial restrictions (see Methods). Sampling frames were restricted for the (i) global, (ii) east-west hemispheric (New World vs. Old World), (iii) biogeographical realm, (iv) tectonic plate, (v) within-realm biome, and (vi) ecoregional extents. Bat communities with positive values of $\mathsf{NRI_{raref_{REL}}}$ and $\mathsf{NTI_{raref_{REL}}}$ indicate that co-occurring species in these communities are phylogenetically related in relation to a given sampling frame extent. Conversely, negative values of NRI and NTI indicate that bat communities are mainly composed of distantly-related species in relation to that given sampling frame extent.

```{r eval=TRUE, echo = FALSE, fig.align = "center", fig.height = 10, fig.width = 16.5, message=FALSE, warning=FALSE}
# MPD.MNTD.LatLong.AllScales.rarefaction.relative.sqrt <- read.csv("data/matrices/MPD.MNTD.LatLong.AllScales.rarefaction.relative.sqrt.csv", h = T)

############################################################################ 
### Representing the phylogenetic community structure of bats across the ###
### gradient of sampling pool (or species pool) restriction              ###
############################################################################

# Representing NRI wrapping across Realms

NRI.Realm.rarefaction.relative.boxplot <- ggplot(filter(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div,
                                                        is.na(ID_Realm) == FALSE),
                                                 aes(x = SamplingPool, 
                                                     y = nri.rarefac.mean)
) +
  geom_boxplot(aes(fill = SamplingPool)) +
  facet_wrap(~ID_Realm,
             nrow = 1,
             strip.position = "bottom") +
  ggsci::scale_fill_uchicago() +
  # scale_fill_nord("baie_mouton", reverse = TRUE) +
  # scale_fill_okabeito(reverse = TRUE) +
  # scale_fill_brewer(palette = "Dark2") +
  # scale_fill_viridis(discrete = TRUE,
  #                    name="Sampling Pool") +
  scale_y_continuous(breaks = round(
    #pretty(MPD.LatLong.AllScales.rarefaction$NRI, n = 7)
    c(min(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div$nri.rarefac.mean, na.rm = T),
      0,
      5,
      10,
      15,
      max(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div$nri.rarefac.mean, na.rm = T))),
    limits = c(min(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div$nri.rarefac.mean, na.rm = T) - 0.1,
               max(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div$nri.rarefac.mean, na.rm = T) + 0.1)
  ) +
  geom_hline(yintercept = 0,
             alpha = 0.4) +
  labs(y="NRI", x = "") +
  theme_minimal() +
  theme_minimal(base_size = 20) +
  theme(strip.background = element_rect(fill = "white",
                                        linetype = NULL,
                                        color = "white"),
        strip.text = element_text(color = "black",
                                  face = "bold",
                                  size = 15),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_blank(),
        axis.title = element_text(size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        legend.title.align = 0.5,
        legend.margin=margin(0, 0, 0, 0),
        legend.box.margin=margin(-5, -5, 2, -5)
  ) +   
  guides(fill = guide_legend(nrow = 1, byrow = TRUE,
                             title.position = "bottom",
                             title = "Lower  ⬅  Sampling Prame Restriction  ➡  Higher",)
  )

NTI.Realm.rarefaction.relative.boxplot <- ggplot(filter(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div,
                                                        is.na(ID_Realm) == FALSE),
                                                 aes(x = SamplingPool, y = nti.rarefac.mean)) +
  geom_boxplot(aes(fill = SamplingPool)) +
  facet_wrap(~ID_Realm,
             nrow = 1,
             strip.position = "bottom") +
  ggsci::scale_fill_uchicago() +
  scale_y_continuous(breaks = pretty(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div$nti.rarefac.mean, n = 5),
                     # round(c(min(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div$nti, na.rm = T),
                     #   0,
                     #   5,
                     #   10,
                     #   15,
                     #   max(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div$nti, na.rm = T)))),
                     limits = c(min(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div$nti.rarefac.mean, na.rm = T) - 0.1,
                                max(MPD.MNTD.Chiroptera.Comm.AllScales.CWM.Div$nti.rarefac.mean, na.rm = T) + 0.1)
  ) +
  geom_hline(yintercept = 0,
             alpha = 0.4) +
  labs(y = "NTI", x = "") +
  theme_minimal(base_size = 20) +
  theme(strip.background = element_rect(fill = "white",
                                        linetype = NULL,
                                        color = "white"),
        strip.text = element_text(color = "black",
                                  face = "bold",
                                  size = 15),
        axis.text.y = element_text(face = "bold"),
        axis.text.x = element_blank(),
        axis.title = element_text(size = 16, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 15),
        legend.title.align = 0.5,
        legend.margin=margin(0, 0, 0, 0),
        legend.box.margin=margin(-5, -5, -5, -5)
  ) +
  guides(fill = guide_legend(nrow = 1, byrow = TRUE,
                             title.position = "bottom",
                             title = "Lower  ⬅  Sampling Frame Restriction  ➡  Higher",)
  )


### Combining plots into a single figure ###

(fig.NRI.NTI.Realm.rarefaction.relative.boxplot <- ggarrange(
  NRI.Realm.rarefaction.relative.boxplot +
    theme(axis.title.x = element_blank()), 
  NTI.Realm.rarefaction.relative.boxplot,
  labels = c("A", "B"),
  ncol = 1, nrow = 2,
  widths = c(1, 1),
  heights = c(1, 1.1),
  align = "v",
  common.legend = TRUE,
  legend = "bottom")
)
```



\noindent 
**Figure S3.3.** Probability contours for the kernel density estimation between paleoclimatic legacies and the sampling frame size bias-corrected rarefied net relatedness index ($\mathsf{NRI_{raref}}$) of worldwide bat communities across sampling frame extents. Paleoclimatic legacies for each bat community were obtained as the historical change in climate since the last glacial maximum (LGM); specifically, the mean annual temperature (MAT) or logarithm of the mean annual precipitation (MAP) from the contemporary period minus the estimated mean annual temperature or logarithm of the mean annual precipitation from 22,000 years ago (see Methods). Bivariate kernel density estimates are represented as the probability contours between the historical changes in temperature (left-column) and precipitation (right-column and) $\mathsf{NRI_{raref}}$ was measured at the (A and B) global, (C and D) east-west hemispheric (New World vs. Old World), (E and F) biogeographical realm, (G and H) tectonic plate, (I and J) within-realm biome, and (K and L) ecoregional sampling frame extents. Lighter tones represent lower quantiles and less frequent combinations while darker tones represent higher quantiles of the probability distribution.

```{r echo=FALSE, eval = FALSE, fig.width = 16.5, fig.height = 7.5*6, fig.align = "center"}
# Combining plots --------------------------------------------

(fig.kde.SamplingPool.NRI.diffTemp.diffPrec <- ggarrange(
  fig.kde.Global.NRI.diff.AnnTemp.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Global.NRI.diff.log.AnnPrec.log.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Hemispheric.NRI.diff.AnnTemp.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Hemispheric.NRI.diff.log.AnnPrec.log.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Realm.NRI.diff.AnnTemp.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Realm.NRI.diff.log.AnnPrec.log.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Plate.NRI.diff.AnnTemp.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Plate.NRI.diff.log.AnnPrec.log.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Biome.NRI.diff.AnnTemp.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Biome.NRI.diff.log.AnnPrec.log.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),  
  fig.kde.Ecoregion.NRI.diff.AnnTemp.LGM_cur.Hpi,
  fig.kde.Ecoregion.NRI.diff.log.AnnPrec.log.LGM_cur.Hpi,
  labels = c("A", "B", 
             "C", "D",
             "E", "F",
             "G", "H",
             "I", "J",
             "K", "L"
  ),
  ncol = 2, nrow = 6,
  widths = c(1, 1),
  heights = c(0.9, 1),
  align = "v",
  font.label = list(size = 28)
)
)
```

\noindent
**Figure S3.4.** Probability contours for the kernel density estimation between paleoclimatic legacies and the sampling frame size bias-corrected rarefied nearest taxon index ($\mathsf{NTI_{raref}}$) of worldwide bat communities across sampling frame extents. Paleoclimatic legacies for each bat community were obtained as the historical change in climate since the last glacial maximum (LGM); specifically, the mean annual temperature (MAT) or logarithm of the mean annual precipitation (MAP) from the contemporary period minus the estimated mean annual temperature or logarithm of the mean annual precipitation from 22,000 years ago (see Methods). Bivariate kernel density estimates are represented as the probability contours between the historical changes in temperature (left-column) and precipitation (right-column and) $\mathsf{NTI_{raref}}$ was measured at the (A and B) global, (C and D) east-west hemispheric (New World vs. Old World), (E and F) biogeographical realm, (G and H) tectonic plate, (I and J) within-realm biome, and (K and L) ecoregional sampling frame extents. Lighter tones represent lower quantiles and less frequent combinations while darker tones represent higher quantiles of the probability distribution.

```{r echo=FALSE, eval = FALSE, fig.width = 16.5, fig.height = 7.5*6, fig.align = "center"}
(fig.kde.SamplingPool.NTI.diffTemp.diffPrec <- ggarrange(
  fig.kde.Global.NTI.diff.AnnTemp.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Global.NTI.diff.log.AnnPrec.log.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Hemispheric.NTI.diff.AnnTemp.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Hemispheric.NTI.diff.log.AnnPrec.log.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Realm.NTI.diff.AnnTemp.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Realm.NTI.diff.log.AnnPrec.log.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Plate.NTI.diff.AnnTemp.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Plate.NTI.diff.log.AnnPrec.log.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Biome.NTI.diff.AnnTemp.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),
  fig.kde.Biome.NTI.diff.log.AnnPrec.log.LGM_cur.Hpi +
    theme(axis.title.x = element_blank()),  
  fig.kde.Ecoregion.NTI.diff.AnnTemp.LGM_cur.Hpi,
  fig.kde.Ecoregion.NTI.diff.log.AnnPrec.log.LGM_cur.Hpi,
  labels = c("A", "B", 
             "C", "D",
             "E", "F",
             "G", "H",
             "I", "J",
             "K", "L"
  ),
  ncol = 2, nrow = 6,
  widths = c(1, 1),
  heights = c(0.9, 1),
  align = "v",
  font.label = list(size = 28)
)
)
```

\noindent
**Figure S3.5.** Relationships between community-weighted mean net diversification rates and the global phylogenetic structure of bat communities [represented by the (A) net relatedness index (NRI) and (B) nearest taxon index (NTI)]. Lines represent significant (P < 0.05) quartic quantile regression estimates for the 5th (lower limits, in lighter tones), 15th, 25th, 35th, 45th, 55th, 65th, 75th, 85th and 95th (upper limits, in darker tones) quantile percentiles of net diversification rates (see Methods and Tables S3 and S4).

[_To be included_]
